Simulating spaces and stressors

### 2024-03-21 Analysis/01_Simulating_spaces_and_stressors.Rmd
Update 01_Simulating_spaces_and_stressors.Rmd

plot.text.box("2) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")

plot.text.box("12) Resampling\nwith stressor:\nequalizing\nmechanism", cex = 2)
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")

plot.text.box("4) Resampling\nwith stressor:\nexcluding\nmechanism", cex = 2)
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D excluding mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D excluding mechanism")

plot.text.box("5) Resampling\nwith stressor:\nfacilitating\nmechanism", cex = 2)
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D facilitation mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D facilitation mechanism")
dev.off()
```

>>>>

plot.text.box("2) Resampling\nwith stressor:\nequalizing\nmechanism", cex = 2)
plot.1D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "1D equalising mechanism")
plot.2D(trait_space, reduction = equalizing_fitness, null = random_reduction, main = "2D equalising mechanism")

plot.text.box("3) Resampling\nwith stressor:\nfacilitating\nmechanism", cex = 2)
plot.1D(trait_space, reduction = facilitation, null = random_reduction, main = "1D facilitation mechanism")
plot.2D(trait_space, reduction = facilitation, null = random_reduction, main = "2D facilitation mechanism")

plot.text.box("4) Resampling\nwith stressor:\nfiltering\nmechanism", cex = 2)
plot.1D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "1D filtering mechanism")
plot.2D(trait_space, reduction = filtering_reduction, null = random_reduction, main = "2D filtering mechanism")

plot.text.box("5) Resampling\nwith stressor:\ncompetition\nmechanism", cex = 2)
plot.1D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "1D competition mechanism")
plot.2D(trait_space, reduction = !competitive_exclusion, null = random_reduction, main = "2D competition mechanism")

dev.off()
```
